Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Add instrumentation mfg info

\caption{\hl {University of New Hampshire (UNH)}-Reference Vertical Axis Turbine (RVAT) turbine model. Turbine blades and struts made from NACA 0020
 profiles with 0.140 m chord. Note that the upper and lower mounting flanges have
 been excluded, as these were included in the tare drag measurements.}

@@

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a Kollmorgen \hl {AKM}
%please define AKM and RPM
  permanent magnet servo \hl {motor (Manufacturer, City, Country)} with a 20:1 gearbox,
providing precise control over shaft angular velocity. This servo was controlled by the tow
tank's main motion controller for high synchronization with the carriage motion,
thereby giving precise measurement and control of the tip speed ratio. An Interface
T8 200 Nm capacity rotary torque \hl {transducer (Manufacturer, City, Country)} was installed inline between the
servo and the turbine, and the servo was also mounted on a slewing ring bearing,
which allowed a redundant measurement of torque via an arm and load cell used to
counteract the turbine moment. The frame was mounted to the carriage via linear
guides, such that the total streamwise drag force was transferred to a pair of
Sentran ZB3 500 pound-force
 capacity S-beam \hl {load cells (Manufacturer, City, Country)}, providing the rotor drag
measurements, after a separately measured tare drag was subtracted in post-processing. Similarly, a tare torque was measured by rotating the turbine shaft
in air. Turbine angular and tow carriage linear position were measured using
quadrature encoder signals, with $10^5$ counts-per-rev for the turbine and 10 ${\mu}$m resolution for the carriage position. These~signals, along with
the torque and drag signals, were sampled at 2 kHz.

>>>>

\caption{University of New Hampshire Reference Vertical Axis Turbine (UNH-RVAT)
    turbine model. Turbine blades and struts made from NACA 0020 profiles with
    0.14~m chord. Note that the upper and lower mounting flanges have been excluded,
    as these were included in the tare drag measurements.}

@@

% Note below: AKM is the model number, not an acronym

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a Kollmorgen AKM permanent magnet servo motor (Kollmorgen, Radford,
VA, USA) with a 20:1 gearbox, providing precise control over shaft angular
velocity. This servo was controlled by the tow tank's main motion controller for
high synchronization with the carriage motion, thereby giving precise
measurement and control of the tip speed ratio. An Interface T8 200 Nm capacity
rotary torque transducer (Interface, Scottsdale, AZ, USA) was installed inline
between the servo and the turbine, and the servo was also mounted on a slewing
ring bearing, which allowed a redundant measurement of torque via an arm and
load cell used to counteract the turbine moment. The frame was mounted to the
carriage via linear guides, such that the total streamwise drag force was
transferred to a pair of Sentran ZB3 500 pound-force capacity S-beam load cells
(Sentran, Santa Ana, CA, USA), providing the rotor drag measurements, after a
separately measured tare drag was subtracted in post-processing. Similarly, a
tare torque was measured by rotating the turbine shaft in air. Turbine angular
and tow carriage linear position were measured using quadrature encoder signals,
with $10^5$ counts-per-rev for the turbine and 10 ${\mu}$m resolution for the
carriage position. These~signals, along with the torque and drag signals, were
sampled at 2 kHz.
